\section{Objective}

Exploit data mining classification algorithms to analyze a real dataset using the RapidMiner machine
learning tool.

\section{Dataset}

The Users dataset (Users.xls) collects census data about American users of a given company. Users are
classified as “basic” or “premium” according to their commonly asked services. Each dataset record
corresponds to a different user. The dataset collects around 32,000 different users, including some
personal user (e.g., age, sex, workclass) as well as their corresponding class. The class attribute, which will
be used as class attribute throughout the practice, is reported as the last record attribute.
\\
The complete list of dataset attributes is reported below:
\begin{enumerate}
    \item Age
    \item Workclass
    \item FlnWgt
    \item Education record
    \item Education-num
    \item Marital status
    \item Occupation
    \item Relationship
    \item Race
    \item Sex
    \item Capital Gain
    \item Capital loss
    \item Hours per week
    \item Native country
    \item class (class attribute)
\end{enumerate}

\section{Context}

Oncologists want to predict the property of recurrence or not of breast tumors according to patient, tumor,
and treatment characteristics. To this purpose, they exploit three different classification algorithms: a
decision tree (Decision Tree) and a Bayesian classifier (Naïve Bayes), and a distance-based classifier (K-NN).
The Breast dataset is used to train classifiers and to validate their performance.